### 2022-01-26 input/experiments.tex
essai decoupage en soussection experiments

This section aims to answer the following questions about \NAME: What
is the overhead of reaching consistent partitioning using \NAME in
large scale networks?  Is \NAME relevant in Edge infrastructures where
\processes are geo-distributed into clusters? We performed the
experimentation using PeerSim, a simulator written in Java that allows
researchers to evaluate and assess distributed algorithms in large
scale networks~\cite{montresor2009peersim}. All the code is available
on the Github platform at
\TODO{\url{https://anonymous.4open.science/r/peersim-partition-5592}}.

@@

\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

\item [Objective:] Confirm that \NAME locks down the traffic of
  decentralized content indexing in the context of dynamic
  inter-autonomous system communications.

@@

\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper.} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.

>>>>

%To answer questions such as: what is the overhead of reaching
%consistent partitioning using \NAME in large scale networks and is
%\NAME relevant in Edge infrastructures where \processes are
%geo-distributed into clusters?
In this section, we discuss the evaluations we conducted on top of
PeerSim, a simulator that allows researchers to
evaluate and assess distributed algorithms in large scale
networks~\cite{montresor2009peersim}. All the code is available on the
Github platform at \url{https://anonymous.4open.science/r/peersim-partition-5592} \note{fix URL}.

@@

\subsection{Scalability}
\begin{asparadesc}
\item [Objective:] Confirm the scalability of \NAME by higlighting the
  trade-off between the current partitioning of the system and the
  protocol's overhead in terms of generated traffic and termination
  time.

@@

\subsection{Trafic containment}
\item [Objective:] Confirm that \NAME locks down the traffic of
  decentralized content indexing in the context of dynamic
  inter-autonomous system communications.

@@

\subsection{Cross \NAME}
\begin{asparadesc}
  \item[Objective:] Highlight the shortcoming of \NAME in Edge
    infrastructures and propose an improvement called \NAMEC (stands
    for \underline{cross} \underline{\NAME}) that enables
    \emph{lazy}\footnote{Laziness properties and \NAMEC would be
    further detailed in the 2 additional pages available for the
    camera-ready version of the paper.} dynamic partitioning by
    allowing gateways to stop notifications when their respective
    network does not appear to have a source.
